---
title: "Object Location Memory: Data Viz & Analysis"
subtitle: <h2>Experiment 2</h2>
author: Mona Zhu
date:  Updated July 25, 2022
output: 
  html_document:
    fig_width: 10
    fig_height: 7
    toc: true
    toc_float: true
    theme: yeti
    highlight: tango
    code_folding: show
---

<style>
pre code, pre, code {
  overflow-y: auto !important;
  max-height: 20em;
}
</style>

```{r setup}
# setting global directory
knitr::opts_chunk$set(fig.show = "asis")
```

```{r load libraries, message=F}
# load libraries
if (!require("pacman")) install.packages("pacman")
pacman::p_load(plyr, openxlsx, reshape2, dplyr, tidyverse, ggplot2, wesanderson, lme4, sjPlot, effects, ggeffects, flextable)

# setting contrast sum as the default model output
options(contrasts=c('contr.sum','contr.poly'))
```

```{r}
plot.customization<-  theme(
    panel.background= element_rect(fill=NA), # transparent panel
    plot.background = element_rect(fill=NA, colour=NA), #transparent background
    panel.grid=element_blank(), # remove panel grid
    axis.ticks.x=element_blank(), # remove tick marks on x-axis
    axis.ticks=element_line(colour="gray70"), # change colour of tick marks
    panel.border = element_rect(fill="transparent", colour="gray70"), # change panel border colour
    legend.background = element_rect(fill = "transparent", colour = "transparent"), # change legend background
    axis.text = element_text(color="gray20"),
    axis.text.x = element_text(size=16),
    text=element_text(size=16),
    axis.title.y = element_text(vjust=1.5),
    legend.key = element_rect(fill = "transparent", colour = "transparent",),
    strip.background = element_rect(color="gray70", fill="transparent", linetype="solid")
    ,legend.position="none"
  )

```

Read cleaned data

```{r}
# load data
df<-read.csv("Word Item Location Memory Cleaned Data (E2)_26Apr2022.csv")

# factorize variables
df$condition<-factor(df$condition, levels = c("Semantic", "Scrambled"))
df$grid.prefer<-factor(df$grid.prefer, levels = c("Semantic", "Scrambled"))
df$block<-factor(recode(df$block, '1'="Block 1", '2'="Block 2"))

# create a variable called "mixup" for looking at substitution 
df$mixup<-ifelse(df$accuracy==0 & df$pos_accuracy==1, 1, 0)

# create subsets for data frames for data analysis
df.error<-subset(df, accuracy==0)

# calculating near error (anything surrounding the target item)
df.error$near.error<-ifelse(df.error$dist<=sqrt(2), 1, 0)

```



# Demographics

```{r}
  df %>%
    reshape2::dcast(randomID+strategy+gender+grid.prefer+age~condition, value.var = "accuracy", mean) %>%
    as.data.frame -> df.sum

# write strategy to file for coding
# write.xlsx(df.sum[c(1,2)], "Object Location Memory E2 Strategy.xlsx", overwrite = F)
```

## Count of Participants

```{r}
folder<- paste0(getwd(), "/Cleaned Data") # folder (or path) that the data is in
locmem.list <- list.files(folder, pattern = "^Location")

paste0("Total Participants Run: ", length(unique(locmem.list)))

paste0("Number of Participants after Exclusion Criteria Applied: ", length(unique(df$randomID)))

```

## Age 

```{r}
paste0("Mean Age of Final Sample: ", round(mean(df.sum$age, na.rm=T),2))

paste0("SD Age of Final Sample: ", round(sd(df.sum$age, na.rm=T),2))
```

## Gender

```{r}
flextable(as.data.frame(table(df.sum$gender, dnn = list("Gender")), responseName = "Count"))
```


# Main Analyses + Data Visuzliation

## Item-Location Binding

### Location Accuracy {.tabset}

Model

```{r}
# overall
# loc.acc1<-glmer(accuracy~condition+(1|randomID)+(1|displayed), family="binomial", data=df,
#                       control = glmerControl(optimizer="bobyqa"))
loc.acc2<-glmer(accuracy~condition+(condition|randomID)+(1|displayed), family="binomial", data=df,
                      control = glmerControl(optimizer="bobyqa"))
# loc.acc3<-glmer(accuracy~condition+(1|randomID)+(condition|displayed), family="binomial", data=df,
#                       control = glmerControl(optimizer="bobyqa"))
# loc.acc4<-glmer(accuracy~condition+(condition|randomID)+(condition|displayed), family="binomial", data=df,
#                       control = glmerControl(optimizer="bobyqa"))

# anova(loc.acc1, loc.acc2) # model 2 is better
# anova(loc.acc1, loc.acc3) # ns
# anova(loc.acc2, loc.acc4) # ns

# mod 2 is best model

# with block
# loc.acc.block1<-glmer(accuracy~condition*block+(1|randomID)+(1|displayed), family="binomial", data=df,
#                       control = glmerControl(optimizer="bobyqa"))
loc.acc.block2<-glmer(accuracy~condition*block+(condition|randomID)+(1|displayed), family="binomial", data=df,
                      control = glmerControl(optimizer="bobyqa"))
# loc.acc.block3<-glmer(accuracy~condition*block+(1|randomID)+(condition|displayed), family="binomial", data=df,
#                       control = glmerControl(optimizer="bobyqa"))
# loc.acc.block4<-glmer(accuracy~condition*block+(condition|randomID)+(condition|displayed), family="binomial", data=df,
#                       control = glmerControl(optimizer="bobyqa"))
# loc.acc.block5<-glmer(accuracy~condition*block+(block|randomID)+(1|displayed), family="binomial", data=df,
#                       control = glmerControl(optimizer="bobyqa"))
# loc.acc.block6<-glmer(accuracy~condition*block+(1|randomID)+(block|displayed), family="binomial", data=df,
#                       control = glmerControl(optimizer="bobyqa")) 
# loc.acc.block7<-glmer(accuracy~condition*block+(condition+block|randomID)+(1|displayed), family="binomial", data=df,
#                       control = glmerControl(optimizer="bobyqa"))

# anova(loc.acc.block1, loc.acc.block2) # model 2 is better
# anova(loc.acc.block1, loc.acc.block3) # ns
# anova(loc.acc.block1, loc.acc.block5) # model 5 better
# anova(loc.acc.block1, loc.acc.block6) # ns
# anova(loc.acc.block2, loc.acc.block5) # model 2 has slightly better AIC and BIC scores

# model 2 best model

tab_model(loc.acc2, loc.acc.block2, transform = NULL, show.stat = T,
          dv.labels = c("Overall", "Block as Factor"))
```

<br>

#### Overall


```{r}
graph1<-ddply(df, c("randomID", "condition"), function(df)
  return(c(dep.avg=mean(df$accuracy))))

graph2<-ddply(graph1, c("condition"), function(df)
  return(c(dep.avg=mean(df$dep.avg), 
           dep.sd=sd(df$dep.avg), 
           dep.count=length(df$dep.avg))))

# png("E2_Location Accuracy.png",
#     width = 200, height = 120, res=300, unit="mm",
#      bg = "white",
#     type = "cairo")

## graph
ggplot(graph2, aes(x=condition, y=dep.avg, colour=condition))+
  geom_point(size=6, shape=17, position = position_dodge(0.5))+
  geom_point(data=graph1, aes(x=condition, y=dep.avg, colour=condition), 
             shape = 16, position=position_jitterdodge(dodge.width=.5, 
                                                       jitter.width = 0.35, 
                                                       jitter.height = 0.01), alpha = 0.25)+
  # geom_line()+
  # stat_smooth(method="glm", method.args=list(family="binomial"), se=FALSE)+
  geom_errorbar(aes(ymax=dep.avg+dep.sd*qt(0.975,df=dep.count-1)/sqrt(dep.count),
                    ymin=dep.avg-dep.sd*qt(0.975,df=dep.count-1)/sqrt(dep.count)),
                width=0.05, position = position_dodge(0.5))+
    plot.customization+

  # scale_colour_manual(labels=c("maroon", "maroon","maroon","maroon"))
  scale_colour_manual("Condition", values=c("Semantic"=wes_palettes$GrandBudapest1[1], 
                                            "Scrambled"=wes_palettes$GrandBudapest2[4]))+
  scale_y_continuous("Proportion Correct (Location Accuracy)", breaks=seq(-1, 1, 0.1))+
  scale_x_discrete("")+
  coord_cartesian(ylim = c(0, 1))
```

#### By Block

```{r}
graph1<-ddply(df, c("randomID", "condition", "block"), function(df)
  return(c(dep.avg=mean(df$accuracy))))

graph2<-ddply(graph1, c("condition", "block"), function(df)
  return(c(dep.avg=mean(df$dep.avg), 
           dep.sd=sd(df$dep.avg), 
           dep.count=length(df$dep.avg))))

# png("E2_Location Accuracy.png",
#     width = 200, height = 120, res=300, unit="mm",
#      bg = "white",
#     type = "cairo")

## graph
ggplot(graph2, aes(x=block, y=dep.avg, colour=condition))+
  geom_point(size=6, shape=17, position = position_dodge(0.5))+
  geom_point(data=graph1, aes(x=block, y=dep.avg, colour=condition), 
             shape = 16, position=position_jitterdodge(dodge.width=.5, 
                                                       jitter.width = 0.35, 
                                                       jitter.height = 0.01), alpha = 0.25)+
  # geom_line()+
  # stat_smooth(method="glm", method.args=list(family="binomial"), se=FALSE)+
  geom_errorbar(aes(ymax=dep.avg+dep.sd*qt(0.975,df=dep.count-1)/sqrt(dep.count),
                    ymin=dep.avg-dep.sd*qt(0.975,df=dep.count-1)/sqrt(dep.count)),
                width=0.05, position = position_dodge(0.5))+
    plot.customization+

  # scale_colour_manual(labels=c("maroon", "maroon","maroon","maroon"))
  scale_colour_manual("Condition", values=c("Semantic"=wes_palettes$GrandBudapest1[1], 
                                            "Scrambled"=wes_palettes$GrandBudapest2[4]))+
  scale_y_continuous("Proportion Correct (Location Accuracy)", breaks=seq(-1, 1, 0.1))+
  scale_x_discrete("")+
  coord_cartesian(ylim = c(0, 1))
```





### Euclidean Distance {.tabset}

Mode:

```{r}
# overall
# euc.dist1<-lmer(dist~condition+(1|randomID)+(1|displayed), data=df,
#                       control = lmerControl(optimizer="bobyqa"))
euc.dist2<-lmer(dist~condition+(condition|randomID)+(1|displayed), data=df,
                      control = lmerControl(optimizer="bobyqa"))
# euc.dist3<-lmer(dist~condition+(1|randomID)+(condition|displayed), data=df,
#                       control = lmerControl(optimizer="bobyqa")) # singular

# anova(euc.dist1, euc.dist2) # model 2 is better model


# model 2 best model

# by block
euc.dist.block1<-lmer(dist~condition*block+(1|randomID) + (1|displayed), data=df,
                      control = lmerControl(optimizer="bobyqa"))
euc.dist.block2<-lmer(dist~condition*block+(condition|randomID) + (1|displayed), data=df,
                      control = lmerControl(optimizer="bobyqa"))
euc.dist.block3<-lmer(dist~condition*block+(1|randomID) + (condition|displayed), data=df,
                      control = lmerControl(optimizer="bobyqa")) # singular
euc.dist.block4<-lmer(dist~condition*block+(block|randomID) + (1|displayed), data=df,
                      control = lmerControl(optimizer="bobyqa"))
euc.dist.block5<-lmer(dist~condition*block+(1|randomID) + (block|displayed), data=df,
                      control = lmerControl(optimizer="bobyqa")) 

# anova(euc.dist.block1, euc.dist.block2) # model 2 is better
# anova(euc.dist.block1, euc.dist.block3) # ns
# anova(euc.dist.block1, euc.dist.block4) # model 4 is better
# anova(euc.dist.block1, euc.dist.block5) # ns
# anova(euc.dist.block2, euc.dist.block4) # model 2 has better AIC / BIC

# model 2 best model


tab_model(euc.dist2, euc.dist.block2, transform = NULL, show.stat = T,
          dv.labels = c("Overall", "Block as Factor"))
```

<p></p>

#### Overall

```{r}
graph1<-ddply(df, c("randomID", "condition"), function(df)
  return(c(dep.avg=mean(df$dist))))

graph2<-ddply(graph1, c("condition"), function(df)
  return(c(dep.avg=mean(df$dep.avg), 
           dep.sd=sd(df$dep.avg), 
           dep.count=length(df$dep.avg))))

# png("E2_Location Accuracy.png",
#     width = 200, height = 120, res=300, unit="mm",
#      bg = "white",
#     type = "cairo")

## graph
ggplot(graph2, aes(x=condition, y=dep.avg, colour=condition))+
  geom_point(size=6, shape=17, position = position_dodge(0.5))+
  geom_point(data=graph1, aes(x=condition, y=dep.avg, colour=condition), 
             shape = 16, position=position_jitterdodge(dodge.width=.5, 
                                                       jitter.width = 0.35, 
                                                       jitter.height = 0.01), alpha = 0.25)+
  # geom_line()+
  # stat_smooth(method="glm", method.args=list(family="binomial"), se=FALSE)+
  geom_errorbar(aes(ymax=dep.avg+dep.sd*qt(0.975,df=dep.count-1)/sqrt(dep.count),
                    ymin=dep.avg-dep.sd*qt(0.975,df=dep.count-1)/sqrt(dep.count)),
                width=0.05, position = position_dodge(0.5))+
    plot.customization+

  # scale_colour_manual(labels=c("maroon", "maroon","maroon","maroon"))
  scale_colour_manual("Condition", values=c("Semantic"=wes_palettes$GrandBudapest1[1], 
                                            "Scrambled"=wes_palettes$GrandBudapest2[4]))+
  scale_y_continuous("Euclidean Distance", breaks=seq(-20, 20, 0.5))+
  scale_x_discrete("")+
  coord_cartesian(ylim = c(0, max(graph1$dep.avg)))
```

#### By Block

```{r}
graph1<-ddply(df, c("randomID", "condition", "block"), function(df)
  return(c(dep.avg=mean(df$dist))))

graph2<-ddply(graph1, c("condition", "block"), function(df)
  return(c(dep.avg=mean(df$dep.avg), 
           dep.sd=sd(df$dep.avg), 
           dep.count=length(df$dep.avg))))

# png("E2_Location Accuracy.png",
#     width = 200, height = 120, res=300, unit="mm",
#      bg = "white",
#     type = "cairo")

## graph
ggplot(graph2, aes(x=block, y=dep.avg, colour=condition))+
  geom_point(size=6, shape=17, position = position_dodge(0.5))+
  geom_point(data=graph1, aes(x=block, y=dep.avg, colour=condition), 
             shape = 16, position=position_jitterdodge(dodge.width=.5, 
                                                       jitter.width = 0.35, 
                                                       jitter.height = 0.01), alpha = 0.25)+
  # geom_line()+
  # stat_smooth(method="glm", method.args=list(family="binomial"), se=FALSE)+
  geom_errorbar(aes(ymax=dep.avg+dep.sd*qt(0.975,df=dep.count-1)/sqrt(dep.count),
                    ymin=dep.avg-dep.sd*qt(0.975,df=dep.count-1)/sqrt(dep.count)),
                width=0.05, position = position_dodge(0.5))+
    plot.customization+

  # scale_colour_manual(labels=c("maroon", "maroon","maroon","maroon"))
  scale_colour_manual("Condition", values=c("Semantic"=wes_palettes$GrandBudapest1[1], 
                                            "Scrambled"=wes_palettes$GrandBudapest2[4]))+
  scale_y_continuous("Euclidean Distance", breaks=seq(-20, 20, 0.5))+
  scale_x_discrete("")+
  coord_cartesian(ylim = c(0, max(graph1$dep.avg)))
```





### Error Distance {.tabset}

Model

```{r}
# overall
error.dist1<-lmer(dist~condition+(1|randomID)+(1|displayed), data=df.error,
                      control = lmerControl(optimizer="bobyqa")) 
# error.dist2<-lmer(dist~condition+(condition|randomID)+(1|displayed), data=df.error,
#                       control = lmerControl(optimizer="bobyqa")) 
# error.dist3<-lmer(dist~condition+(1|randomID)+(condition|displayed), data=df.error,
#                       control = lmerControl(optimizer="bobyqa")) #singular

# anova(error.dist1, error.dist2) # ns

# model 1 is best model

# by block
error.dist.block1<-lmer(dist~condition*block+(1|randomID)+(1|displayed), data=df.error,
                      control = lmerControl(optimizer="bobyqa"))
# error.dist.block2<-lmer(dist~condition*block+(condition|randomID)+(1|displayed), data=df.error,
#                       control = lmerControl(optimizer="bobyqa"))
# error.dist.block3<-lmer(dist~condition*block+(1|randomID)+(condition|displayed), data=df.error,
#                       control = lmerControl(optimizer="bobyqa")) # singular
# error.dist.block4<-lmer(dist~condition*block+(block|randomID)+(1|displayed), data=df.error,
#                       control = lmerControl(optimizer="bobyqa")) 
# error.dist.block5<-lmer(dist~condition*block+(1|randomID)+(block|displayed), data=df.error,
#                       control = lmerControl(optimizer="bobyqa")) # singular

# anova(error.dist.block1, error.dist.block2) # ns
# anova(error.dist.block1, error.dist.block4) # ns

# model 1 best model

tab_model(error.dist1, error.dist.block1, transform = NULL, show.stat = T,
          dv.labels = c("Overall", "Block as Factor"))
```

<p></p>

#### Overall

```{r}
graph1<-ddply(df.error, c("randomID", "condition"), function(df)
  return(c(dep.avg=mean(df$dist))))

graph2<-ddply(graph1, c("condition"), function(df)
  return(c(dep.avg=mean(df$dep.avg), 
           dep.sd=sd(df$dep.avg), 
           dep.count=length(df$dep.avg))))

# png("E2_Location Accuracy.png",
#     width = 200, height = 120, res=300, unit="mm",
#      bg = "white",
#     type = "cairo")

## graph
ggplot(graph2, aes(x=condition, y=dep.avg, colour=condition))+
  geom_point(size=6, shape=17, position = position_dodge(0.5))+
  geom_point(data=graph1, aes(x=condition, y=dep.avg, colour=condition), 
             shape = 16, position=position_jitterdodge(dodge.width=.5, 
                                                       jitter.width = 0.35, 
                                                       jitter.height = 0.01), alpha = 0.25)+
  # geom_line()+
  # stat_smooth(method="glm", method.args=list(family="binomial"), se=FALSE)+
  geom_errorbar(aes(ymax=dep.avg+dep.sd*qt(0.975,df=dep.count-1)/sqrt(dep.count),
                    ymin=dep.avg-dep.sd*qt(0.975,df=dep.count-1)/sqrt(dep.count)),
                width=0.05, position = position_dodge(0.5))+
    plot.customization+

  # scale_colour_manual(labels=c("maroon", "maroon","maroon","maroon"))
  scale_colour_manual("Condition", values=c("Semantic"=wes_palettes$GrandBudapest1[1], 
                                            "Scrambled"=wes_palettes$GrandBudapest2[4]))+
  scale_y_continuous("Error Distance", breaks=seq(-20, 20, 0.5))+
  scale_x_discrete("")+
  coord_cartesian(ylim = c(1, max(graph1$dep.avg)))
```

#### By Block

```{r}
graph1<-ddply(df.error, c("randomID", "condition", "block"), function(df)
  return(c(dep.avg=mean(df$dist))))

graph2<-ddply(graph1, c("condition", "block"), function(df)
  return(c(dep.avg=mean(df$dep.avg), 
           dep.sd=sd(df$dep.avg), 
           dep.count=length(df$dep.avg))))

# png("E2_Location Accuracy.png",
#     width = 200, height = 120, res=300, unit="mm",
#      bg = "white",
#     type = "cairo")

## graph
ggplot(graph2, aes(x=block, y=dep.avg, colour=condition))+
  geom_point(size=6, shape=17, position = position_dodge(0.5))+
  geom_point(data=graph1, aes(x=block, y=dep.avg, colour=condition), 
             shape = 16, position=position_jitterdodge(dodge.width=.5, 
                                                       jitter.width = 0.35, 
                                                       jitter.height = 0.01), alpha = 0.25)+
  # geom_line()+
  # stat_smooth(method="glm", method.args=list(family="binomial"), se=FALSE)+
  geom_errorbar(aes(ymax=dep.avg+dep.sd*qt(0.975,df=dep.count-1)/sqrt(dep.count),
                    ymin=dep.avg-dep.sd*qt(0.975,df=dep.count-1)/sqrt(dep.count)),
                width=0.05, position = position_dodge(0.5))+
    plot.customization+

  # scale_colour_manual(labels=c("maroon", "maroon","maroon","maroon"))
  scale_colour_manual("Condition", values=c("Semantic"=wes_palettes$GrandBudapest1[1], 
                                            "Scrambled"=wes_palettes$GrandBudapest2[4]))+
  scale_y_continuous("Error Distance", breaks=seq(-20, 20, 0.5))+
  scale_x_discrete("")+
  coord_cartesian(ylim = c(1, max(graph1$dep.avg)))
```




### Substitution 

```{r}
mixup.mod0<-glmer(mixup~condition+(1|randomID), family = "binomial", data=df.error,
                  control = glmerControl(optimizer="bobyqa")) 
# mixup.mod1<-glmer(mixup~condition+(1|randomID)+(1|displayed), family = "binomial", data=df.error,
#                   control = glmerControl(optimizer="bobyqa")) # singular

# model 0 best model


mixup.block.mod0<-glmer(mixup~condition*block+(1|randomID), family = "binomial", data=df.error,
                  control = glmerControl(optimizer="bobyqa"))
# mixup.block.mod1<-glmer(mixup~condition*block+(1|randomID)+(1|displayed), family = "binomial", data=df.error,
#                   control = glmerControl(optimizer="bobyqa")) # singular

# model 0 is best model

tab_model(mixup.mod0, mixup.block.mod0, transform = NULL, show.stat = T,
          dv.labels = c("Overall", "By Block"))
```


#### Overall


```{r}
graph1<-ddply(df.error, c("randomID", "condition"), function(df)
  return(c(dep.avg=mean(df$mixup))))

graph2<-ddply(graph1, c("condition"), function(df)
  return(c(dep.avg=mean(df$dep.avg), 
           dep.sd=sd(df$dep.avg), 
           dep.count=length(df$dep.avg))))

# png("E2_Location Accuracy.png",
#     width = 200, height = 120, res=300, unit="mm",
#      bg = "white",
#     type = "cairo")

## graph
ggplot(graph2, aes(x=condition, y=dep.avg, colour=condition))+
  geom_point(size=6, shape=17, position = position_dodge(0.5))+
  geom_point(data=graph1, aes(x=condition, y=dep.avg, colour=condition), 
             shape = 16, position=position_jitterdodge(dodge.width=.5, 
                                                       jitter.width = 0.35, 
                                                       jitter.height = 0.01), alpha = 0.25)+
  # geom_line()+
  # stat_smooth(method="glm", method.args=list(family="binomial"), se=FALSE)+
  geom_errorbar(aes(ymax=dep.avg+dep.sd*qt(0.975,df=dep.count-1)/sqrt(dep.count),
                    ymin=dep.avg-dep.sd*qt(0.975,df=dep.count-1)/sqrt(dep.count)),
                width=0.05, position = position_dodge(0.5))+
    plot.customization+

  # scale_colour_manual(labels=c("maroon", "maroon","maroon","maroon"))
  scale_colour_manual("Condition", values=c("Semantic"=wes_palettes$GrandBudapest1[1], 
                                            "Scrambled"=wes_palettes$GrandBudapest2[4]))+
  scale_y_continuous("Proportion of Substitution Errors", breaks=seq(-1, 1, 0.1))+
  scale_x_discrete("")+
  coord_cartesian(ylim = c(0, 1))
```

#### By Block

```{r}
graph1<-ddply(df.error, c("randomID", "condition", "block"), function(df)
  return(c(dep.avg=mean(df$mixup))))

graph2<-ddply(graph1, c("condition", "block"), function(df)
  return(c(dep.avg=mean(df$dep.avg), 
           dep.sd=sd(df$dep.avg), 
           dep.count=length(df$dep.avg))))

# png("E2_Location Accuracy.png",
#     width = 200, height = 120, res=300, unit="mm",
#      bg = "white",
#     type = "cairo")

## graph
ggplot(graph2, aes(x=block, y=dep.avg, colour=condition))+
  geom_point(size=6, shape=17, position = position_dodge(0.5))+
  geom_point(data=graph1, aes(x=block, y=dep.avg, colour=condition), 
             shape = 16, position=position_jitterdodge(dodge.width=.5, 
                                                       jitter.width = 0.35, 
                                                       jitter.height = 0.01), alpha = 0.25)+
  # geom_line()+
  # stat_smooth(method="glm", method.args=list(family="binomial"), se=FALSE)+
  geom_errorbar(aes(ymax=dep.avg+dep.sd*qt(0.975,df=dep.count-1)/sqrt(dep.count),
                    ymin=dep.avg-dep.sd*qt(0.975,df=dep.count-1)/sqrt(dep.count)),
                width=0.05, position = position_dodge(0.5))+
    plot.customization+

  # scale_colour_manual(labels=c("maroon", "maroon","maroon","maroon"))
  scale_colour_manual("Condition", values=c("Semantic"=wes_palettes$GrandBudapest1[1], 
                                            "Scrambled"=wes_palettes$GrandBudapest2[4]))+
  scale_y_continuous("Proportion of Substitution Errors", breaks=seq(-1, 1, 0.1))+
  scale_x_discrete("")+
  coord_cartesian(ylim = c(0, 1))
```


### Near Errors


```{r}
nearfar.mod1<-glmer(near.error~condition+(1|randomID)+(1|displayed), family = "binomial", data=df.error,
                  control = glmerControl(optimizer="bobyqa"))
# nearfar.mod2<-glmer(near.error~condition+(condition|randomID)+(1|displayed), family = "binomial", data=df.error,
#                   control = glmerControl(optimizer="bobyqa"))
# nearfar.mod3<-glmer(near.error~condition+(1|randomID)+(condition|displayed), family = "binomial", data=df.error,
#                   control = glmerControl(optimizer="bobyqa")) # singular

# anova(nearfar.mod1, nearfar.mod2) # ns
# model 1 is best model


nearfar.block.mod1<-glmer(near.error~condition*block+(1|randomID)+(1|displayed), family = "binomial", data=df.error,
                  control = glmerControl(optimizer="bobyqa"))
# nearfar.block.mod2<-glmer(near.error~condition*block+(condition|randomID)+(1|displayed), family = "binomial", data=df.error,
#                   control = glmerControl(optimizer="bobyqa"))
# nearfar.block.mod3<-glmer(near.error~condition*block+(1|randomID)+(condition|displayed), family = "binomial", data=df.error,
#                   control = glmerControl(optimizer="bobyqa")) # singular
# nearfar.block.mod4<-glmer(near.error~condition*block+(block|randomID)+(1|displayed), family = "binomial", data=df.error,
#                   control = glmerControl(optimizer="bobyqa")) 
# nearfar.block.mod5<-glmer(near.error~condition*block+(1|randomID)+(block|displayed), family = "binomial", data=df.error,
#                   control = glmerControl(optimizer="bobyqa")) # singular

# anova(nearfar.block.mod1, nearfar.block.mod2) # ns
# anova(nearfar.block.mod1, nearfar.block.mod4) # ns

# model 1 is best model

tab_model(nearfar.mod1,nearfar.block.mod1, transform = NULL, show.stat = T,
          dv.labels = c("Overall", "By Block"))
```


#### Overall


```{r}
graph1<-ddply(df.error, c("randomID", "condition"), function(df)
  return(c(dep.avg=mean(df$near.error))))

graph2<-ddply(graph1, c("condition"), function(df)
  return(c(dep.avg=mean(df$dep.avg), 
           dep.sd=sd(df$dep.avg), 
           dep.count=length(df$dep.avg))))

# png("E2_Location Accuracy.png",
#     width = 200, height = 120, res=300, unit="mm",
#      bg = "white",
#     type = "cairo")

## graph
ggplot(graph2, aes(x=condition, y=dep.avg, colour=condition))+
  geom_point(size=6, shape=17, position = position_dodge(0.5))+
  geom_point(data=graph1, aes(x=condition, y=dep.avg, colour=condition), 
             shape = 16, position=position_jitterdodge(dodge.width=.5, 
                                                       jitter.width = 0.35, 
                                                       jitter.height = 0.01), alpha = 0.25)+
  # geom_line()+
  # stat_smooth(method="glm", method.args=list(family="binomial"), se=FALSE)+
  geom_errorbar(aes(ymax=dep.avg+dep.sd*qt(0.975,df=dep.count-1)/sqrt(dep.count),
                    ymin=dep.avg-dep.sd*qt(0.975,df=dep.count-1)/sqrt(dep.count)),
                width=0.05, position = position_dodge(0.5))+
    plot.customization+

  # scale_colour_manual(labels=c("maroon", "maroon","maroon","maroon"))
  scale_colour_manual("Condition", values=c("Semantic"=wes_palettes$GrandBudapest1[1], 
                                            "Scrambled"=wes_palettes$GrandBudapest2[4]))+
  scale_y_continuous("Proportion of Near Errors", breaks=seq(-1, 1, 0.1))+
  scale_x_discrete("")+
  coord_cartesian(ylim = c(0, 1))
```

#### By Block

```{r}
graph1<-ddply(df.error, c("randomID", "condition", "block"), function(df)
  return(c(dep.avg=mean(df$near.error))))

graph2<-ddply(graph1, c("condition", "block"), function(df)
  return(c(dep.avg=mean(df$dep.avg), 
           dep.sd=sd(df$dep.avg), 
           dep.count=length(df$dep.avg))))

# png("E2_Location Accuracy.png",
#     width = 200, height = 120, res=300, unit="mm",
#      bg = "white",
#     type = "cairo")

## graph
ggplot(graph2, aes(x=block, y=dep.avg, colour=condition))+
  geom_point(size=6, shape=17, position = position_dodge(0.5))+
  geom_point(data=graph1, aes(x=block, y=dep.avg, colour=condition), 
             shape = 16, position=position_jitterdodge(dodge.width=.5, 
                                                       jitter.width = 0.35, 
                                                       jitter.height = 0.01), alpha = 0.25)+
  # geom_line()+
  # stat_smooth(method="glm", method.args=list(family="binomial"), se=FALSE)+
  geom_errorbar(aes(ymax=dep.avg+dep.sd*qt(0.975,df=dep.count-1)/sqrt(dep.count),
                    ymin=dep.avg-dep.sd*qt(0.975,df=dep.count-1)/sqrt(dep.count)),
                width=0.05, position = position_dodge(0.5))+
    plot.customization+

  # scale_colour_manual(labels=c("maroon", "maroon","maroon","maroon"))
  scale_colour_manual("Condition", values=c("Semantic"=wes_palettes$GrandBudapest1[1], 
                                            "Scrambled"=wes_palettes$GrandBudapest2[4]))+
  scale_y_continuous("Proportion of Near Errors", breaks=seq(-1, 1, 0.1))+
  scale_x_discrete("")+
  coord_cartesian(ylim = c(0, 1))
```





## Metacognition

### Display Preference

```{r}
table(df.sum$grid.prefer)
chisq.test(table(df.sum$grid.prefer))
```

```{r}
df.sum %>%
  group_by(grid.prefer) %>%
  dplyr::summarise(count=n()) %>%
  ungroup() %>%
  dplyr::mutate(total=sum(count), prop=count/total) %>%
  as.data.frame() -> pref.table
```





```{r}
ggplot(pref.table, aes(x="Display Preference", y=prop, fill=grid.prefer))+
  geom_bar(stat="identity", position = "fill")+
  plot.customization+
  scale_fill_manual("", values=c("Semantic"=wes_palettes$GrandBudapest1[1],
                                            "Scrambled"=wes_palettes$GrandBudapest2[4]))+
  scale_y_continuous("Proportion", breaks=seq(0, 1, 0.1))+
  scale_x_discrete("")
```


### Display Preference as a function of Task Performance

#### T-Test

```{r}
df.sum$semantic.advantage<-df.sum$Semantic-df.sum$Scrambled

t.test(df.sum$semantic.advantage~df.sum$grid.prefer)
```



```{r}
graph2<-ddply(df.sum, c("grid.prefer"), function(df)
  return(c(dep.avg=mean(df$semantic.advantage, na.rm=T), 
           dep.sd=sd(df$semantic.advantage, na.rm = T), 
           dep.count=length(df$semantic.advantage))))

# png("E2_Location Accuracy.png",
#     width = 200, height = 120, res=300, unit="mm",
#      bg = "white",
#     type = "cairo")

## graph
ggplot(graph2, aes(x=grid.prefer, y=dep.avg, colour=grid.prefer))+
  geom_point(size=6, shape=17, position = position_dodge(0.5))+
  geom_point(data=df.sum, aes(x=grid.prefer, y=semantic.advantage, colour=grid.prefer), 
             shape = 16, position=position_jitterdodge(dodge.width=.5, 
                                                       jitter.width = 0.35, 
                                                       jitter.height = 0.01), alpha = 0.25)+
  geom_errorbar(aes(ymax=dep.avg+dep.sd*qt(0.975,df=dep.count-1)/sqrt(dep.count),
                    ymin=dep.avg-dep.sd*qt(0.975,df=dep.count-1)/sqrt(dep.count)),
                width=0.05, position = position_dodge(0.5))+
    plot.customization+
  scale_colour_manual("Condition", values=c("Semantic"=wes_palettes$GrandBudapest1[1], 
                                            "Scrambled"=wes_palettes$GrandBudapest2[4]))+
  scale_y_continuous("Semantic Advantage\n(Semantic - Scrambled)", breaks=seq(-1, 1, 0.1))+
  scale_x_discrete("Display Preference")+
  geom_hline(yintercept = 0, linetype="longdash", colour="grey70")

```

#### Logistic Regression

Running this analysis to better understand the inflection point

```{r}
df.sum$grid.prefer.num<-ifelse(df.sum$grid.prefer=="Semantic", 1, 0)

gridprefer.mod<-glm(grid.prefer.num~semantic.advantage, family = "binomial", data=df.sum)
tab_model(gridprefer.mod, show.stat = T, transform = NULL)

```


```{r}
ggplot(df.sum, aes(x=semantic.advantage, y=grid.prefer.num))+ 
  geom_jitter(width = 0.05, height = 0.05, alpha=0.2)+
  stat_smooth(method="glm", method.args=list(family="binomial"), se=FALSE)+
  plot.customization+
  # scale_colour_manual(labels=c("maroon", "maroon","maroon","maroon"))
  geom_hline(yintercept = .5, linetype="dotted")+
  geom_vline(xintercept = c(0, -0.139) , linetype="dotted")+
  scale_x_continuous("Semantic Advantage\n(Semantic - Scrambled)", breaks=seq(-1, 1, 0.1))+
  scale_y_continuous("Display Preference\n(1 = Semantic; 0 = Scrambled)", breaks=seq(-1, 1, 0.1))+
  coord_cartesian(ylim = c(0, 1)) 
```























